---
title: "Chapter 4 Exercises"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(itsmr)
```

#### Periodogram Example


```{r, echo=FALSE}
par(mfrow=c(3,2))
plot(Sunspots,type='l')
periodogram(Sunspots,opt=2)
plot(airpass,type='l')
periodogram(airpass,opt=2)
plot(wine,type='l')
periodogram(wine,opt=2)
```

#### Exercise 4.2

```{r}
z <- rnorm(100,mean=0,sd=(2*pi)**.5)
periodogram(z,rep(1,10))
```

#### Exercise 4.7

```{r}
yw_sunspots <- yw(Sunspots,2)
plots(yw_sunspots)
print(c('Phi 1',yw_sunspots$phi[1]))
print(c('Phi 2',yw_sunspots$phi[2]))
print(c('Sigma Squared',yw_sunspots$sigma2))
```

Following the process of example 4.4.1 we see the model takes its maximum frequency where $cos(\lambda)=\frac{(\phi_1 \phi_2-\phi_1)}{4\phi_2}$. This is equal to .848, or $\lambda=.55$ radians. The period is equal to $\frac{1}{\lambda / 2 \pi}=11.3$, or oe cycle equaling 11.3 years.

#### Exercise 4.8

```{r}
ar_3 <- specify(ar=c(0,0,.99))
plots(ar_3)
```

The spectral density plot above would suggest that we see oscillatory behaviour. This is because of the very high frequency around 2. This is equivalent to a period of approximately three years.

```{r}
set.seed(1)
simulated_data <- sim(ar_3,60)
plotc(simulated_data)
```

This graph supports the conclusion reached in part b of oscillating behaviour with a period of 3.

```{r}
smooth_simulated_data <- smooth.ma(simulated_data,1)
plotc(simulated_data,smooth_simulated_data)
periodogram(smooth_simulated_data)
```

